Formalizing Stack Safety as a Security Property

### 2023-02-03 submission5/core.tex
pass on 6

We implement and test two micro-policies from Roessler and DeHon \cite{}:
{\em Depth Isolation} (\(DI\)) and {\em Lazy Tagging and Clearing} (\(LTC\)).
They share a common structure: each function activation is assigned a ``color'' \(n\)
representing its identity. Stack locations belonging to that activation are
tagged \(\tagStackDepth{n}\), and when it is active, the tag on the
program counter (PC tag) is \(\tagPCDepth{n}\). The tag \(\tagNoDepth\)
is for stack locations that are currently unused.

In \(DI\), \(n\) always corresponds to the depth of the stack when
the function is called. A functions must initialize its entire frame on a call
in order to tag it, and then clear it on a return.
During normal execution, the micro-policy rules only permit load and
store operations when the target memory is tagged {\em with the same depth}
as the current {\PCname} tag, and store operations also when the
target memory is \(\tagNoDepth\).

In \(LTC\), rather than initialize the entire frame,
a function will initialize each location's tag when it writes to it. It does
not check if those writes are legal! If the PC tag is \(\tagPCDepth{n}\),
then any stack location that recieves a store will be tagged \(\tagStackDepth{n}\).
On a load, the micro-policy failstops if the value that it would load
is tagged \(\tagStackDepth{n}\) or \(\tagNoDepth\) and the PC tag doesn't
match \(n\).

\paragraph{Blessed Sequences}

To implement this discipline, {\em blessed instruction sequences} appear at
the entry and exit of each function, which manipulate tags as just described
while performing the usual tasks of saving/restoring the return address to/from
the stack and adjusting the stack pointer. A blessed sequence also guarantees
that the full sequence executes from the beginning---no jumping into the middle.

\paragraph{Protecting Registers}

Roessler and DeHon do not protect registers, but we consider registers to be
an extension of the stack. In particular, \(\clri\) requires callee-saved
registers to be saved and restored properly. We extend \(DI\) and \(LTC\)
so that callee-saved registers, too, are tagged with the color of the 
function that is using them. In \(DI\) they are tagged as part of the entry
sequence, while in \(LTC\) they are tagged when a value is placed in them.

>>>>

We implement and test two micro-policies from Roessler and DeHon~\cite{DBLP:conf/sp/RoesslerD18}:
{\em Depth Isolation} (\(DI\)) and {\em Lazy Tagging and Clearing} (\(LTC\)).
They share a common structure: each function activation is assigned a ``color'' \(n\)
representing its identity. Stack locations belonging to that activation are
tagged \(\tagStackDepth{n}\), and while the activation is running, the tag on the
program counter (PC tag) is \(\tagPCDepth{n}\). Stack locations not part of
any activation are tagged \(\tagNoDepth\).

In \(DI\), \(n\) always corresponds to the depth of the stack when
the function is called. A function must initialize its entire frame upon entry
in order to tag it, and then clear the frame before returning.
During normal execution, the micro-policy rules only permit load and
store operations when the target memory is tagged {\em with the same depth}
as the current {\PCname} tag, or, for store operations, if the target memory
is tagged \(\tagNoDepth\).

In \(LTC\), rather than initialize the entire frame at entry,
a function initializes each location's tag when it writes to it. It does
not check if those writes are legal! If the PC tag is \(\tagPCDepth{n}\),
then any stack location that recieves a store will be tagged \(\tagStackDepth{n}\).
On a load, the micro-policy failstops if the source memory location 
is tagged \(\tagNoDepth\) or \(\tagStackDepth{n}\) for some \(n\) that
doesn't match the PC tag.

\paragraph*{Blessed Sequences}

To implement this discipline, {\em blessed instruction sequences} appear at
the entry and exit of each function, which manipulate tags as just described
while performing the usual tasks of saving/restoring the return address to/from
the stack and adjusting the stack pointer. A blessed sequence uses further tags
to guarantee that the full sequence executes from the beginning---no jumping into the middle.

\paragraph*{Protecting Registers}

Roessler and DeHon do not protect registers, but we consider registers to be
an extension of the stack. In particular, \(\clri\) requires callee-saved
registers to be saved and restored properly. We extend \(DI\) and \(LTC\)
so that callee-saved registers, too, are tagged with the color of the 
function that is using them. In \(DI\) they are tagged as part of the entry
sequence, while in \(LTC\) they are tagged when a value is placed in them.
\apt{Presumably R\&dH don't care about registers because they already have
  the compiler in the TCB.  We should not (perhaps earlier than here!) that
  we have a stronger attacker model since we don't require the callee code
  to come from a trusted  compiler.}
